---
title: "RIPA"
author: "Shuo Chen"
date: "10/9/2020"
output: html_document
---

```{r}
library(tidyverse)
library(lubridate)
```



```{r}
ripa <- read_csv("RIPAStopData_2018.csv")
```


```{r}
ripa %>% 
  group_by(AGENCY_NAME) %>% 
  summarize(stop_by_agency = n()) %>% 
  arrange(desc(stop_by_agency))
```



## date and time
```{r}
ripa %>% 
  mutate(stop_hr = str_sub(TIME_OF_STOP, 1, 2), 
         stop_min = str_sub(TIME_OF_STOP, 3, 4)) -> ripa
```

# only run once
```{r}
ripa %>% 
  mutate(HR_OF_STOP = str_sub(TIME_OF_STOP, 1, 2),
         MIN_OF_STOP = str_sub(TIME_OF_STOP, -2, -1),
         TIME_OF_STOP = str_c(HR_OF_STOP, ":", MIN_OF_STOP),
         DATE_OF_STOP = str_remove_all(DATE_OF_STOP, " 0:00:00")
         ) -> ripa
```


```{r}
ripa %>% 
  mutate(DATE_TIME_OF_STOP = str_c(DATE_OF_STOP, " ", TIME_OF_STOP),
         DATE_TIME_OF_STOP = mdy_hm(DATE_TIME_OF_STOP),
         HR_OF_STOP = hour(DATE_TIME_OF_STOP),
         MIN_OF_STOP = minute(DATE_TIME_OF_STOP)
         ) -> ripa

ripa %>% 
  select(TIME_OF_STOP, DATE_OF_STOP, DATE_TIME_OF_STOP, HR_OF_STOP, MIN_OF_STOP)
```


## race 5 categories (1: Asian, 2: Black, 3: Hispanic, 7: White, 9: Other)
```{r}
ripa %>% 
  mutate(RAE5 = case_when(
    RAE_FULL == 1 ~ 1, 
    RAE_FULL == 2 ~ 2,
    RAE_FULL == 3 ~ 3,
    RAE_FULL == 7 ~ 7,
    RAE_FULL == 4 | RAE_FULL == 5 | RAE_FULL == 6 | RAE_FULL == 8 ~ 9
  )) -> ripa

ripa %>% count(RAE_FULL)
ripa %>% count(RAE5)
```


## Total Searches by age group
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 |ADS_SEARCH_PROPERTY) %>% 
  group_by(AGENCY_ORI_2, AGE_GROUP) %>% 
  summarize(n_srch = n()) %>% 
  print(n = 72)

```


## Overall reason for stop by Race 

```{r}
ripa %>% 
  group_by(RAE_FULL) %>% 
  summarize(prop_traffic = sum(REASON_FOR_STOP == 1)/n(), 
            prop_sus = sum(REASON_FOR_STOP == 2)/n(),
            prop_other = sum(REASON_FOR_STOP > 2)/n(),
            n_traffic = sum(REASON_FOR_STOP == 1), 
            n_sus = sum(REASON_FOR_STOP == 2),
            n_other = sum(REASON_FOR_STOP > 2))
```


## reason for stop by agency and race 
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(prop_traffic = sum(REASON_FOR_STOP == 1)/n(), 
            prop_sus = sum(REASON_FOR_STOP == 2)/n(),
            prop_other = sum(REASON_FOR_STOP > 2)/n(),
            n_traffic = sum(REASON_FOR_STOP == 1), 
            n_sus = sum(REASON_FOR_STOP == 2),
            n_other = sum(REASON_FOR_STOP > 2)) %>% 
  print(n = 64)

```


# Overall Search rates by race
```{r}
ripa %>% 
  group_by( RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) 
```


## SEARCH RATES by race and agency
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```

## Overall Search Rate, by race, 18-24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1, na.rm = TRUE))
```


## Overall search rates, by race, 25-34

```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```


## Overall search rates, by race, 35-44

```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```

## Overall search rates, by race, over 45

```{r}
ripa %>% 
  filter(AGE_GROUP == 7) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```


## search rates, by race AND AGENCY, 18 - 24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1, na.rm = TRUE)) %>% 
  print(n = 64)
```


## search rates, by race and agency,  25 - 34
```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```


## search rates,by race and agency, 35 - 44
```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```

## search rates,by race and agency, 45 and above
```{r}
ripa %>% 
  filter(AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```



# OVERALL HIT RATES BY RACE 
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY) %>% 
  group_by(RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```


### HIT RATES BY AGENCY & RACE 
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY) %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```


## Overall Hit rates by race and age group 

```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY) %>% 
  group_by(AGE_GROUP, RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 18 - 24
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY ==1, AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 25 - 34
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY ==1, AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates,by race and agency, 35 - 44
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 45 and above
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY ==1, AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```











# CONSENT SEARCH
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON, 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON == 1, 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 18 - 24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON, 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON == 1, 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```


## consent search, 25 - 34
```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON, 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON == 1, 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 35 - 44
```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON, 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON == 1, 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 45 and above
```{r}
ripa %>% 
  filter(AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON, 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN == 1 & ADS_SEARCH_PERSON == 1, 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```


# CONSET SEARCH HIT RATES
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1, BFS_CONSENT_GIVEN == 1) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_FIREARM == 1 | CED_AMMUNITION == 1 | CED_WEAPON == 1  | 
                             CED_DRUGS == 1  | CED_ALCOHOL == 1  | CED_MONEY == 1  | 
                             CED_DRUG_PARAPHERNALIA == 1  | CED_STOLEN_PROP == 1  | 
                             CED_ELECT_DEVICE == 1  | CED_OTHER_CONTRABAND == 1 )/n()) %>% 
  print(n = 64)

```


## consent searches hit rates, 18 - 24
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_FIREARM == 1 | CED_AMMUNITION == 1 | CED_WEAPON == 1  | 
                             CED_DRUGS == 1  | CED_ALCOHOL == 1  | CED_MONEY == 1  | 
                             CED_DRUG_PARAPHERNALIA == 1  | CED_STOLEN_PROP == 1  | 
                             CED_ELECT_DEVICE == 1  | CED_OTHER_CONTRABAND == 1 )/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 25 - 34
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_FIREARM == 1 | CED_AMMUNITION == 1 | CED_WEAPON == 1  | 
                             CED_DRUGS == 1  | CED_ALCOHOL == 1  | CED_MONEY == 1  | 
                             CED_DRUG_PARAPHERNALIA == 1  | CED_STOLEN_PROP == 1  | 
                             CED_ELECT_DEVICE == 1  | CED_OTHER_CONTRABAND == 1 )/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 35 - 44
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_FIREARM == 1 | CED_AMMUNITION == 1 | CED_WEAPON == 1  | 
                             CED_DRUGS == 1  | CED_ALCOHOL == 1  | CED_MONEY == 1  | 
                             CED_DRUG_PARAPHERNALIA == 1  | CED_STOLEN_PROP == 1  | 
                             CED_ELECT_DEVICE == 1  | CED_OTHER_CONTRABAND == 1 )/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 45 and above
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON == 1, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_FIREARM == 1 | CED_AMMUNITION == 1 | CED_WEAPON == 1  | 
                             CED_DRUGS == 1  | CED_ALCOHOL == 1  | CED_MONEY == 1  | 
                             CED_DRUG_PARAPHERNALIA == 1  | CED_STOLEN_PROP == 1  | 
                             CED_ELECT_DEVICE == 1  | CED_OTHER_CONTRABAND == 1 )/n()) %>% 
  print(n = 64)

```



