---
title: "RIPA"
author: "Shuo Chen"
date: "10/9/2020"
output: html_document
---

```{r}
library(tidyverse)
library(lubridate)
```



```{r}
ripa <- read_csv("C:/Users/shuoc/Documents/Berkeley/2020_Fall/data_science/mid_term/RIPA Stop Data 2018.csv")
```


```{r}
ripa %>% 
  group_by(AGENCY_NAME) %>% 
  summarize(stop_by_agency = n()) %>% 
  arrange(desc(stop_by_agency))
```



## date and time
```{r}
ripa %>% 
  mutate(stop_hr = str_sub(TIME_OF_STOP, 1, 2), 
         stop_min = str_sub(TIME_OF_STOP, 3, 4)) -> ripa
```

# only run once
```{r}
ripa %>% 
  mutate(HR_OF_STOP = str_sub(TIME_OF_STOP, 1, 2),
         MIN_OF_STOP = str_sub(TIME_OF_STOP, -2, -1),
         TIME_OF_STOP = str_c(HR_OF_STOP, ":", MIN_OF_STOP),
         DATE_OF_STOP = str_remove_all(DATE_OF_STOP, " 0:00:00")
         ) -> ripa
```


```{r}
ripa %>% 
  mutate(DATE_TIME_OF_STOP = str_c(DATE_OF_STOP, " ", TIME_OF_STOP),
         DATE_TIME_OF_STOP = mdy_hm(DATE_TIME_OF_STOP),
         HR_OF_STOP = hour(DATE_TIME_OF_STOP),
         MIN_OF_STOP = minute(DATE_TIME_OF_STOP)
         ) -> ripa

ripa %>% 
  select(TIME_OF_STOP, DATE_OF_STOP, DATE_TIME_OF_STOP, HR_OF_STOP, MIN_OF_STOP)
```


## race 5 categories (1: Asian, 2: Black, 3: Hispanic, 7: White, 9: Other)
```{r}
ripa %>% 
  mutate(RAE5 = case_when(
    RAE_FULL == 1 ~ 1, 
    RAE_FULL == 2 ~ 2,
    RAE_FULL == 3 ~ 3,
    RAE_FULL == 7 ~ 7,
    RAE_FULL == 4 | RAE_FULL == 5 | RAE_FULL == 6 | RAE_FULL == 8 ~ 9
  )) -> ripa

ripa %>% count(RAE_FULL)
ripa %>% count(RAE5)
```



## AGE5
```{r}
ripa %>% 
  mutate(AGE4 = case_when(
    AGE_GROUP >= 1 & AGE_GROUP <= 4 ~ 4,
    AGE_GROUP == 5 ~ 5,
    AGE_GROUP == 6 ~ 6,
    AGE_GROUP >= 7 & AGE_GROUP <= 9 ~ 7
  )) -> ripa

ripa %>% count(AGE_GROUP)
ripa %>% count(AGE4)
```


### Number of Stops by Agency
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2) %>% 
  summarize(n_srch = n())
```


## Total Searches by age group
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON |ADS_SEARCH_PROPERTY) %>% 
  group_by(AGENCY_ORI_2, AGE_GROUP) %>% 
  summarize(n_srch = n()) %>% 
  print(n = 72)

```


## Overall reason for stop by Race 

```{r}
ripa %>% 
  group_by(RAE_FULL) %>% 
  summarize(prop_traffic = sum(REASON_FOR_STOP == 1)/n(), 
            prop_sus = sum(REASON_FOR_STOP == 2)/n(),
            prop_other = sum(REASON_FOR_STOP > 2)/n(),
            n_traffic = sum(REASON_FOR_STOP == 1), 
            n_sus = sum(REASON_FOR_STOP == 2),
            n_other = sum(REASON_FOR_STOP > 2))
```


## reason for stop by agency and race 
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(prop_traffic = sum(REASON_FOR_STOP == 1)/n(), 
            prop_sus = sum(REASON_FOR_STOP == 2)/n(),
            prop_other = sum(REASON_FOR_STOP > 2)/n(),
            n_traffic = sum(REASON_FOR_STOP == 1), 
            n_sus = sum(REASON_FOR_STOP == 2),
            n_other = sum(REASON_FOR_STOP > 2)) %>% 
  print(n = 64)

```


# Overall Search rates by race
```{r}
ripa %>% 
  group_by( RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1 | ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) 
```

# search rates by race excluding CHP
```{r}
ripa %>% 
  filter(AGENCY_ORI_2 != 4) %>% 
  group_by( RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 
```


## Overall Search Rates by Reason for Stop and Race
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, AGENCY_ORI_2 != 4) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 
```


## Overall Search Rates and Hit Rates by Reason for Stop, Race, 18 - 24
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 4) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 


ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
         REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 4) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n())
```


## Overall Search Rates and Hit Rates by Reason for Stop, Race, 25 - 34
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 5) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 


ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
         REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 5) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n())
```


## Overall Search Rates and Hit Rates by Reason for Stop, Race, 35 - 44
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 6) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 


ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
         REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP == 6) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n())
```


## Overall Search Rates and Hit Rates by Reason for Stop, Race, 45 and above
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP >= 7) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, na.rm = TRUE)) 


ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
         REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2, 
         AGENCY_ORI_2 != 4, AGE_GROUP >= 7) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n())
```


### Traffic violation search rate plot
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1, 
         AGENCY_ORI_2 != 4, 
         RAE5 == 2 | RAE5 == 3 | RAE5 == 7) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
                              na.rm = TRUE)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = search_rate, color = as.factor(RAE5))) +
  geom_line() +
  labs(title = "Minority Drivers are More Likely to be Searched during Traffic Stops",
       x = "age group", y = "search rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(search_rate, digits=2), 1), 
                vjust = -0.3), size = 3.5) +
  scale_color_discrete(labels = c("African American", "Hispanic", "White")) +
  scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent, 
                     limits = c(0, 0.3),
                     breaks = seq(0, 0.3, by = 0.1))
```


### Traffic violation hit rate plot
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1, 
         AGENCY_ORI_2 != 4, 
         ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
         RAE5 == 2 | RAE5 == 3 | RAE5 == 7) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = hit_rate, color = as.factor(RAE5))) +
  geom_line() +
  labs(title = "Minority Drivers Stopped for Traffic Violations Have Lower Hit Rates",
       x = "age group", y = "hit rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(hit_rate, digits=2), 1), 
                vjust = -0.3), size = 3.5) +  
  scale_color_discrete(labels = c("African American", "Hispanic", "White")) +
    scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.3),
                     breaks = seq(0, 0.3, by = 0.1))
```




## Overall Hit Rates by Reason for Stop and Race
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, AGENCY_ORI_2 != 4,
         REASON_FOR_STOP == 1 | REASON_FOR_STOP == 2) %>% 
  group_by(REASON_FOR_STOP, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n(), 
            n_hit = sum(CED_NONE_CONTRABAND==0))


```






## SEARCH RATES by race and agency
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(), 
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```

## Overall Search Rate, by race, 18-24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```


## Overall search rates, by race, 25-34

```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```


## Overall search rates, by race, 35-44

```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```

## Overall search rates, by race, over 45

```{r}
ripa %>% 
  filter(AGE_GROUP == 7) %>% 
  group_by(RAE_FULL) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE))
```


## search rates, by race AND AGENCY, 18 - 24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```


## search rates, by race and agency,  25 - 34
```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```


## search rates,by race and agency, 35 - 44
```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```

## search rates,by race and agency, 45 and above
```{r}
ripa %>% 
  filter(AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)/n(),
            n_search = sum(ADS_SEARCH_PERSON == 1| ADS_SEARCH_PROPERTY ==1, na.rm = TRUE)) %>% 
  print(n = 64)
```



# OVERALL HIT RATES BY RACE 
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY) %>% 
  group_by(RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n())

```


### HIT RATES BY AGENCY & RACE 
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY) %>% 
  group_by(AGENCY_ORI_2, RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```


## Overall Hit rates by race and age group 

```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY) %>% 
  group_by(AGE_GROUP, RAE_FULL) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 18 - 24
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 25 - 34
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates,by race and agency, 35 - 44
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```


## hit rates, by race and agency, 45 and above
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)
```











# CONSENT SEARCH
```{r}
ripa %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY), 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON| ADS_SEARCH_PROPERTY), 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 18 - 24
```{r}
ripa %>% 
  filter(AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY), 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON| ADS_SEARCH_PROPERTY), 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```


## consent search, 25 - 34
```{r}
ripa %>% 
  filter(AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY), 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON| ADS_SEARCH_PROPERTY), 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 35 - 44
```{r}
ripa %>% 
  filter(AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY), 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON| ADS_SEARCH_PROPERTY), 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```

## consent search, 45 and above
```{r}
ripa %>% 
  filter(AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(consent_srch_rate = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY), 
                                    na.rm = TRUE)/n(), 
            n_tot_consent = sum(BFS_CONSENT_GIVEN & (ADS_SEARCH_PERSON| ADS_SEARCH_PROPERTY), 
                                na.rm = TRUE)) %>% 
  print(n = 64)
```


# CONSET SEARCH HIT RATES
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, BFS_CONSENT_GIVEN == 1) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```


## consent searches hit rates, 18 - 24
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP == 4) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 25 - 34
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, BFS_CONSENT_GIVEN == 1,  
         AGE_GROUP == 5) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 35 - 44
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, BFS_CONSENT_GIVEN == 1, 
         AGE_GROUP == 6) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```

## consent searches hit rates, 45 and above
```{r}
ripa %>% 
  filter(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, BFS_CONSENT_GIVEN == 1,
         AGE_GROUP >= 7) %>% 
  group_by(AGENCY_ORI_2, RAE5) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0)/n()) %>% 
  print(n = 64)

```



