---
title: "RIPA Presentation Plots"
output:
  html_document:
    df_print: paged
---
```{r}
library(tidyverse)
library(lubridate)
library(scales)
library(tidyverse)
library(dplyr)
library(readr)
library(lubridate)
```
##import RIPA dataset
```{r}
ripa <- read_csv("RIPA Stop Data 2018.csv")
```
##generate 5 race/ethnic groups (factored)
```{r}
ripa %>% 
  mutate(RAE5 = case_when(
    RAE_FULL == 1 ~ "Asian", 
    RAE_FULL == 2 ~ "Black",
    RAE_FULL == 3 ~"Hispanic",
    RAE_FULL == 7 ~ "White",
    RAE_FULL == 4 | RAE_FULL == 5 | RAE_FULL == 6 | RAE_FULL == 8 ~ "Other"
  )) ->ripa
```
##establish for age groups (factored)
```{r}
ripa %>% 
  mutate(AGE4 = case_when(
    AGE_GROUP >= 1 & AGE_GROUP <= 4 ~ 4,
    AGE_GROUP == 5 ~ 5,
    AGE_GROUP == 6 ~ 6,
    AGE_GROUP >= 7 & AGE_GROUP <= 9 ~ 7
  )) -> ripa
ripa %>% count(AGE_GROUP)
ripa %>% count(AGE4)
```
##population pyramid: # of stops by Race and Gender
```{r}
ripa %>%
  filter(G_MALE == 1 | G_FEMALE == 1)%>%
  group_by(RAE5,G_MALE)%>%
ggplot(mapping=aes(x = fct_infreq(as.factor(RAE5)), fill = as.factor(G_MALE))) + 
  geom_bar(data=subset(ripa, G_MALE==1)) + 
  geom_bar(data=subset(ripa,G_MALE==0),aes( y=..count..*(-1))) + scale_y_continuous(breaks = seq(-200000, 550000, 50000), labels=abs(seq(-200, 550, 50))) +  coord_flip() +
  # Flip axes
  labs(title="Number of Stops by Race and Gender", y="number of stops (in thousands)", x="race & ethnicity", fill="Gender") + 
  theme(plot.title = element_text(hjust = .5), axis.title=element_blank(),
 axis.ticks = element_blank(), legend.title=element_blank()) + theme_bw() +  scale_fill_manual(values=c("#E69F00","#56B4E9"),labels = c("Women", "Men"))
```
##bar chart: distribution of agency stops:
```{r}
ripa %>%
  group_by(AGENCY_ORI_2)%>%
  ggplot(aes(x=as.factor(AGENCY_ORI_2), y=..prop.., group=1)) + geom_histogram(stat = "count", fct_relevel=(c("3","4","6","5","7","8","1","2")))+theme_minimal()+labs() + theme(axis.line = element_line(colour = "white"),axis.text.y=element_blank(),
        axis.ticks.y=element_blank(), axis.title.x=element_blank(),axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),legend.position = "none") + scale_x_discrete(guide = guide_axis(n.dodge = 2), labels=c("1"="LA Sheriff","2"="LAPD", "3"="Riverside Sheriff", "4"= "CHP","5"="San Bern. Sheriff", "6"="SD Sheriff", "7"= "SDPD","8"="SFPD"))+geom_text(aes(label=scales::percent(round(..prop..,2)), y=..prop..), stat="count", vjust=-.5, size=3)
```

##bar chart:stop rates by reason for stop and race/ethnicity groups

```{r}
ripa %>% 
  group_by(RAE5,REASON_FOR_STOP) %>% 
  mutate(REASON_FOR_STOP = case_when(
    REASON_FOR_STOP == 1 ~ "Traffic Violation", 
    REASON_FOR_STOP == 2 ~ "Reasonable Suspicion",
    REASON_FOR_STOP >= 3 ~"Other")) %>%
  mutate(prop_stop=sum(REASON_FOR_STOP==2,na.rm = TRUE)/n())%>% 
  mutate(RAE5=fct_relevel(RAE5,"Black", "Hispanic", "White", "Other","Asian"))%>%
ggplot(mapping=aes(x=RAE5, fill=REASON_FOR_STOP)) + 
    geom_bar(position="fill")+ theme_minimal() + theme(axis.line = element_line(colour = "black"),axis.text.y=element_blank(),
        axis.ticks.y=element_blank(), axis.title.x=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) + scale_fill_manual(values=c("#56B4E9", "#009E73", "#0072B2")) + labs(y = "Stop Rate", fill="Reason For Stop", label="white") + scale_y_continuous(labels = scales::percent)
```
##create use of force variable
```{r}
ripa %>% 
  mutate(use_of_force = case_when(ADS_FIREARM_POINT == 1 
                            | ADS_FIREARM_DISCHARGE== 1
                            | ADS_ELECT_DEVICE== 1
                            | ADS_IMPACT_DISCHARGE ==1 
                            | ADS_CANINE_BITE == 1 
                            | ADS_BATON == 1 
                            | ADS_CHEM_SPRAY == 1
                            | ADS_OTHER_CONTACT == 1 ~ 1, 
  ADS_FIREARM_POINT == 0 
  & ADS_FIREARM_DISCHARGE== 0
  & ADS_ELECT_DEVICE== 0 
  & ADS_IMPACT_DISCHARGE ==0 
  & ADS_CANINE_BITE == 0 
  & ADS_BATON == 0
  & ADS_CHEM_SPRAY == 0
  & ADS_OTHER_CONTACT== 0 ~ 0 )) -> ripa
```
##box plot: use of force rates by race/ethnicity group 
```{r}
ripa %>% 
  group_by(RAE5,AGE4) %>% 
  
  summarize(force_rate= sum(use_of_force, na.rm = TRUE)/n()) %>% 
  ggplot(aes(x = reorder(as.factor(RAE5), -force_rate), y = force_rate, fill = as.factor(RAE5))) +
  geom_boxplot() +
  labs(title = "Officers More Likely to Use Force on Black Individuals",
  x=" ", y = "use of force rate", color = "Race/Ethnicity") +scale_color_discrete(labels = c("Asian", "Black", "Hispanic", "White", "Other")) +scale_fill_discrete(name=NULL) + theme(legend.title = element_blank()) + theme_minimal()+ 
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.02),
                     breaks = seq(0, 0.02, by = 0.005))
```

##line graph/facet wrap: search rates by race/ethnicity and age groups

```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
                              na.rm = TRUE)/n()) %>% mutate(RAE5=fct_relevel(RAE5,"Black", "Hispanic", "White", "Other","Asian"))%>% 
  ggplot(mapping = aes(x = AGE4, y = search_rate, color = as.factor(RAE5))) +
  geom_line() +
  labs(title = "Black and Hispanic Drivers More Likely to be Searched during Traffic Stops",
       x = "age group", y = "search rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(search_rate, digits=2), 1), 
                vjust = -0.3), size = 2.0) +
  scale_x_continuous(label = c("<24", "25-34", 
                               "35-44", ">45")) +facet_wrap(~RAE5)+
  scale_y_continuous(labels = scales::percent, 
                     limits = c(0, 0.3),
                     breaks = seq(0, 0.3, by = 0.1)) + theme_minimal()
```


### Overall search rate plot
```{r}
ripa %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
                              na.rm = TRUE)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = search_rate, color = as.factor(RAE5))) +
  geom_line() +
  theme_classic() +
  labs(title = "Overall Search Rates",
       x = "age group", y = "search rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(search_rate, digits=2), 1), 
                vjust = -0.3), size = 3) +
  scale_color_discrete(labels = c("Asian", "Black", "Hispanic", 
                                  "White", "Other")) +
  scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent, 
                     limits = c(0, 0.3),
                     breaks = seq(0, 0.3, by = 0.05))
```



### Traffic violation stop hit rate plot
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 1,
         ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0, na.rm = TRUE)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = hit_rate, color = as.factor(RAE5))) +
  geom_line() +
  theme_classic() +
  labs(title = "Traffic Violations Stop Hit Rates",
       x = "age group", y = "hit rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(hit_rate, digits=2), 1), 
                vjust = -0.3), size = 3) +  
  scale_color_discrete(labels = c("Asian", "Black", "Hispanic", 
                                  "White", "Other")) +
    scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.3),
                     breaks = seq(0, 0.3, by = 0.1))
```


### Reasonable suspicion stop search rate plot
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 2) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(search_rate = sum(ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY, 
                              na.rm = TRUE)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = search_rate, color = as.factor(RAE5))) +
  geom_line() +
  theme_classic() +
  labs(title = "Reasonable Suspicion Stop Search Rates",
       x = "age group", y = "search rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(search_rate, digits=2), 1), 
                vjust = -0.3), size = 3) +
  scale_color_discrete(labels = c("Asian", "Black", "Hispanic", 
                                  "White", "Other")) +
  scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent, 
                     limits = c(0, 0.6),
                     breaks = seq(0, 0.6, by = 0.1))
```


### Reasonable suspicion stop hit rate plot
```{r}
ripa %>% 
  filter(REASON_FOR_STOP == 2, 
         ADS_SEARCH_PERSON | ADS_SEARCH_PROPERTY) %>% 
  group_by(RAE5, AGE4) %>% 
  summarize(hit_rate = sum(CED_NONE_CONTRABAND==0, na.rm = TRUE)/n()) %>% 
  ggplot(mapping = aes(x = AGE4, y = hit_rate, color = as.factor(RAE5))) +
  geom_line() +
  theme_classic() +
  labs(title = "Reasonable Suspicion Stop Hit Rates",
       x = "age group", y = "hit rate", color = "Race/Ethnicity") +
  geom_text(aes(label = scales::percent(round(hit_rate, digits=2), 1), 
                vjust = -0.3), size = 3) +  
  scale_color_discrete(labels = c("Asian", "Black", "Hispanic", 
                                  "White", "Other")) +
    scale_x_continuous(label = c("24 and younger", "25 to 34", 
                               "35 to 44", "45 and older")) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.4),
                     breaks = seq(0, 0.4, by = 0.1))
